The `geomnet` package

### 2020-11-19 README.Rmd
fixing little issues as i prepare for release

<!-- README.md is generated from README.Rmd. Please edit that file -->
[![CRAN Status](http://www.r-pkg.org/badges/version/geomnet)](https://cran.r-project.org/package=geomnet)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/geomnet)](http://www.r-pkg.org/pkg/geomnet)
[![Travis-CI Build Status](https://travis-ci.org/sctyner/geomnet.svg?branch=master)](https://travis-ci.org/sctyner/geomnet)

>>>>

<!-- README.md is generated from README.Rmd. Please edit that file -->
[![CRAN Status](http://www.r-pkg.org/badges/version/geomnet)](https://cran.r-project.org/package=geomnet)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/geomnet)](https://www.r-pkg.org/pkg/geomnet)
[![Travis-CI Build Status](https://travis-ci.org/sctyner/geomnet.svg?branch=master)](https://travis-ci.org/sctyner/geomnet)
